{\helveticaitalic{Supplementary Material}}

### 2022-03-08 tex/manuscript.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  We derive conditions that describe period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for
    increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
    solutions. Dashed lines show the interval between the $5-5$ and the suppressed
    solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals
    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in
    $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
    $ISI$s with the free phase. During the free phase, $ISI$s are of approximately
    constant duration $T$.\label{fig:bif-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of
    the three branches (A, B, C) also shows the timecourse of the total synaptic
    conductance $\gbar s$ of a sample stable solution of both cells (blue and orange),
    as well as the release conductance $g^{\star}$ (dashed green line).
    $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet
    cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with
    a long release delay associated with a subset of $2-2$ solutions. Here the release
    condition is briefly satisfied after the first spike of cell 1. This does not cause
    firing of cell 2, which only occurs after the second spike of cell 1.
    $\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is
    approximately zero and the release condition is sufficient for firing of cell 2.
    ~\label{fig:release-delay}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
    Each continuous branch is associated with a stable $n-n$ burst solution. Increasing
    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T$.~\label{fig:delta-t}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from
    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
    \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of
    the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

>>>>

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  We derive conditions that describe period-increment bifurcations between stable $n:n$ and $(n+1):(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable $n:n$ solutions for
    increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
    solutions. Dashed lines show the interval between the $5-5$ and the suppressed
    solutions, where higher period $n:n$ solutions occur on increasingly smaller intervals
    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n:n$ solutions in
    $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
    $ISI$s with the free phase. During the free phase, $ISI$s are of approximately
    constant duration $T$.\label{fig:bif-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of
    the three branches (A, B, C) also shows the timecourse of the total synaptic
    conductance $\gbar s$ of a sample stable solution of both cells (blue and orange),
    as well as the release conductance $g^{\star}$ (dashed green line).
    $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet
    cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with
    a long release delay associated with a subset of $2-2$ solutions. Here the release
    condition is briefly satisfied after the first spike of cell 1. This does not cause
    firing of cell 2, which only occurs after the second spike of cell 1.
    $\bm{\mathrm{(C)}}$ Branch with $n:n$ solutions  where release delay is
    approximately zero and the release condition is sufficient for firing of cell 2.
    ~\label{fig:release-delay}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T$.~\label{fig:delta-t}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
    \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of
    the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

### 2022-03-08 tex/sections/discussion.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

% MAIN RESULTS
To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression. When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns. Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$. This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively. Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons. Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs. The results from our one-dimensional map match excellently with numerical simulation of the full network. Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.

% FURTHER METHOD IDEAS
We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical. However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes. It is conceivable that our map construction can be extended to also capture such $m-n$ solutions. Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables. To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other. To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$. While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}. Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons. As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses. In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.

@@

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased. That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength. We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$. We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}. It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}. Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity. The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods. In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations. It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system. In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

% FLOW SYSTEM BIFURCATION
In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions. While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points. However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
% Should be possible to use averaging to reduce the system.

>>>>

% MAIN RESULTS
To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression. When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n:n$ burst patterns. Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$. This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n:n$ solutions respectively. Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons. Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n:n$ burst solutions of the full two-cell system of ODEs. The results from our one-dimensional map match excellently with numerical simulation of the full network. Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.

% FURTHER METHOD IDEAS
We have studied $n:n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical. However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes. It is conceivable that our map construction can be extended to also capture such $m-n$ solutions. Remember, in the case of symmetrical coupling with $n:n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables. To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other. To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$. While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}. Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons. As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses. In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.

@@

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n:n$ solutions lose robustness as their period is increased. That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength. We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$. We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}. It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}. Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity. The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods. In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations. It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system. In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

% FLOW SYSTEM BIFURCATION
In addition to stable $n:n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n:n$ solutions. While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points. However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
% Should be possible to use averaging to reduce the system.

### 2022-03-08 tex/sections/introduction.tex
Refactor a bunch of plots
Change notation from n-n to n:n
This is what reviewer 1 suggested.

~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
inhibitory depressing synapses.  Numerical simulations showed that when the reciprocal
synaptic conductance between the two neurons is varied, the network produces symmetric
\(n-n\) anti-phase bursts, with stronger synaptic coupling leading to longer bursts.  They
used methods from geometric singular perturbation theory to separate the timescales of the
fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional
conditions necessary for the existence of stable \(n-n\) solutions (for \(n\leq 2\)).
According to these conditions the type of firing pattern largely depends on the slow
depression dynamics of the synapses between the two neurons, and can therefore be
predicted by knowing the strengths of the synaptic conductances of the two synapses.
Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
identify the type of stable \(n-n\) pattern for any given value of the coupling strength.
However, they do not predict the exact period of such solutions.  Furthermore, while they
provide good arguments for the validity of their reduction assumptions and the resulting
scalar conditions, they do not verify them numerically.

Here we extend the previous analysis by providing a Poincaré map of the slow depression
dynamics.  This allows us not only to predict the types of stable \(n-n\) solutions the full
network can produce, (for any \(n\)), but also to study how varying the coupling strength
affects the period of such solutions.  To do this, we build on, and numerically test, the
assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.  We reduce the
two-cell model to a scalar Poincaré map that tracks the evolution of the depression from
the beginning of one burst to the beginning of the next burst.  Stable fixed points of our
map are associated with stable \(n-n\) burst solutions.  Our map construction is motivated
by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007},
which approximates the anti-phase bursting dynamics of a network of two coupled
Morris-Lecar neurons.  In contrast to our model, the network described in
the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst
termination is instead accomplished through the dynamics of a slow T-type calcium current.

% MAIN RESULTS AND CONCLUSIONS
The Poincaré map derived here replicates the results from numerical simulations of the
full two-cell ODE system: Given the strength of maximum conductance between the two
neurons, fixed points of our map predict the type and period of \(n-n\) patterns, the switch
between burst solutions of different periods, as well as the occurrence of co-existent
solutions.  In addition to proving the existence and stability of fixed points, our map
shows that fixed points are created via a fold bifurcation of maps.  We also derive
algebraic conditions that predict the period increment bifurcations that allow the switch
between \(n-n\) and \((n+1)-(n+1)\) solutions.  Because our map is fully explicit, it lays the
framework for studying the effects of other model parameter on network dynamics without
the need to run expensive numerical integrations of the ODEs.

% PAPER STRUCTURE.
This paper is organised as follows.  First, we introduce the network of two neurons, and
describe the properties of single cell and synapse dynamics.  We use numerical simulations
of the network to provide an intuition for the range of possible burst dynamics the system
can produce.  Next, we state and justify the simplifying assumptions that are necessary
for the map construction.  Finally, we analytically derive the first return map of the
depression variable as well as the conditions that are required for stable solutions to
bifurcate between \(n-n\) and \((n+1)-(n+1)\) solutions.  We end this work with a discussion.

>>>>

~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
inhibitory depressing synapses.
Numerical simulations showed that when the reciprocal synaptic conductance between the two neurons is varied, the network produces symmetric $n:n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.
They used methods from geometric singular perturbation theory to separate the timescales of the fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional conditions necessary for the existence of stable $n:n$ solutions (for $n\leq 2$).
According to these conditions the type of firing pattern largely depends on the slow
depression dynamics of the synapses between the two neurons, and can therefore be
predicted by knowing the strengths of the synaptic conductances of the two synapses.
Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
identify the type of stable $n:n$ pattern for any given value of the coupling strength.
However, they do not predict the exact period of such solutions.
Furthermore, while they provide good arguments for the validity of their reduction assumptions and the resulting scalar conditions, they do not verify them numerically.

Here we extend the previous analysis by providing a Poincaré map of the slow depression
dynamics.
This allows us not only to predict the types of stable $n:n$ solutions the full
network can produce, (for any $n$), but also to study how varying the coupling strength
affects the period of such solutions.
To do this, we build on, and numerically test, the
assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.
We reduce the two-cell model to a scalar Poincaré map that tracks the evolution of the depression from the beginning of one burst to the beginning of the next burst.
Stable fixed points of our map are associated with stable $n:n$ burst solutions.
Our map construction is motivated by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007}, which approximates the anti-phase bursting dynamics of a network of two coupled Morris-Lecar neurons.
In contrast to our model, the network described in the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst termination is instead accomplished through the dynamics of a slow T-type calcium current.

% MAIN RESULTS AND CONCLUSIONS
The Poincaré map derived here replicates the results from numerical simulations of the
full two-cell ODE system: Given the strength of maximum conductance between the two
neurons, fixed points of our map predict the type and period of $n:n$ patterns, the switch
between burst solutions of different periods, as well as the occurrence of co-existent
solutions.
In addition to proving the existence and stability of fixed points, our map shows that fixed points are created via a fold bifurcation of maps.
We also derive algebraic conditions that predict the period increment bifurcations that allow the switch between $n:n$ and $(n+1):(n+1)$ solutions.
Because our map is fully explicit, it lays the framework for studying the effects of other model parameter on network dynamics without the need to run expensive numerical integrations of the ODEs.

% PAPER STRUCTURE.
This paper is organised as follows.
First, we introduce the network of two neurons, and describe the properties of single cell and synapse dynamics.
We use numerical simulations of the network to provide an intuition for the range of possible burst dynamics the system can produce.
Next, we state and justify the simplifying assumptions that are necessary for the map construction.
Finally, we analytically derive the first return map of the depression variable as well as the conditions that are required for stable solutions to bifurcate between $n:n$ and $(n+1):(n+1)$ solutions.
We end this work with a discussion.

### 2022-03-08 tex/sections/methods.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

When the total inhibitory conductance $g = \bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
In case of no inhibition ($g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
In the case of a non-zero inhibition ($g>0$) the location of $v_{\infty}$ depends on the exact value of $g$.
Increasing $g$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
When $g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
In the following section we will refer to the value of the total conductance at the bifurcation as $g_{HB}$.

The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}. The following mathematical analysis is performed on the equations of a single cell. Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.

>>>>

When the total inhibitory conductance $g = \bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
In case of no inhibition ($g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
In the case of a non-zero inhibition ($g>0$) the location of $v_{\infty}$ depends on the exact value of $g$.
Increasing $g$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
When $g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
In the following section we will refer to the value of the total conductance at the bifurcation as $g_{bif}$.

The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
The following mathematical analysis is performed on the equations of a single cell.
Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
% TODO: Edit this later
It should be noted that \citep{bose2011} used $n-n$ to denote the stable bursts with $n$ spikes, however, here we use the $n:n$ notation for more clarity.
